Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
lr editing

For technical reasons (monotonicity of the logical relation), a
temporary region is not removed in the model when it is
revoked. Instead it is turned into a new kind of region, namely a
revoked region. A revoked region contains no state transition
system and puts no requirements on the memory it models. It serves
simply as a mask for a temporary region that have been revoked.
(This way of masking a region goes back to earlier work of
Ahmed~\cite{Ahmed2004semantics} and was also used in~\cite{Thamsborg:2011:KLR:2034773.2034831}.)

% Recursive worlds intuition
The worlds end up being recursive. The memory can contain capabilities
and capabilities grants authority over part of the memory. A world
models memory, so it also needs to be able to model capabilities in
memory and the protocols on them. Whether a capability satisfies the
protocol of a region may depend on what it grants authority over in
memory which is described by the world.

% Short technical explanation
The recursiveness of the worlds gives rise to a recurisve domain
equation. Theorem~\ref{thm:world-existence} gives the solution to this
recursive domain equation.
\begin{theorem}\label{thm:world-existence}
  There exists a \cofe{} $\Wor$ and preorders $\futurestr$ and
  $\futurewk$ such that $(\Wor,\futurestr)$ and $(\Wor,\futurewk)$ are
  preordered \cofes{}, and there exists an isomorphism $\xi$ such that
  {\small
    \begin{align*}              
      \xi : \Wor & \cong \blater (\nats \finparfun \Regions)\\
      \Regions & = \{\revoked\} \uplus \\
                 &\hskip -2cm \{\temp\} \times \States \times \Rels \times (\States \fun (\Wor \monwknefun \UPred{\HeapSegments})) \uplus \\
                 & \hskip -2cm \{\perma\} \times \States \times \Rels \times (\States \fun (\Wor \monstrnefun \UPred{\HeapSegments}))
    \end{align*}
  } and for $W, W' \in \Wor$
  \begin{align*}
    W' \futurestr W & \Leftrightarrow \xi(W') \futurestr \xi(W)   \\
    W' \futurewk W & \Leftrightarrow \xi(W') \futurewk \xi(W)
  \end{align*}
\end{theorem}
We use the $\Regions$ from Theorem~\ref{thm:world-existence} to define
the worlds:
\begin{align*}
  \Worlds & = \RegionNames \finparfun \Regions\\
 \RegionNames & = \nats
\end{align*}

>>>>

For technical reasons (monotonicity of the logical relation), a
temporary region is not removed in the model when it is
revoked. Instead it is turned into a new kind of region, namely a
revoked region. A revoked region contains no state transition
system and puts no requirements on the memory it models. It
simply serves as a mask for a temporary region that have been revoked.
This way of masking a region goes back to earlier work of
Ahmed~\cite{Ahmed2004semantics} and was also used in~\cite{Thamsborg:2011:KLR:2034773.2034831}.

% Recursive worlds intuition
% The worlds end up being defined recursively: The memory can contain
% capabilities,
% which grant authority over parts of memory. A world
% models memory, so it also needs to be able to model capabilities in
% memory and the protocols on them. Whether a capability satisfies the
% protocol of a region may depend on what it grants authority over in
% memory which is described by the world.

The worlds end up being defined recursively: Worlds describe memory,
which can contain capabilities, whose safety depends on worlds. 
We use the method of Birkedal et
al.~\cite{Birkedal:2011:SKM:1926385.1926401} 
for constructing the worlds.

% Short technical explanation
% The recursiveness of the worlds gives rise to a recurisve domain
% equation. Theorem~\ref{thm:world-existence} gives the solution to this
% recursive domain equation.
\begin{theorem}\label{thm:world-existence}
  There exists a \cofe{} $\Wor$ and preorders $\futurestr$ and
  $\futurewk$ such that $(\Wor,\futurestr)$ and $(\Wor,\futurewk)$ are
  preordered \cofes{}, and there exists an isomorphism $\xi$ such that
  {\small
    \begin{align*}              
      \xi : \Wor & \cong \blater (\nats \finparfun \Regions)\\
      \Regions & = \{\revoked\} \uplus \\
                 &\hskip -2cm \{\temp\} \times \States \times \Rels \times (\States \fun (\Wor \monwknefun \UPred{\HeapSegments})) \uplus \\
                 & \hskip -2cm \{\perma\} \times \States \times \Rels \times (\States \fun (\Wor \monstrnefun \UPred{\HeapSegments}))
    \end{align*}
  } and for $W, W' \in \Wor$
  \begin{align*}
    W' \futurestr W & \Leftrightarrow \xi(W') \futurestr \xi(W)   \\
    W' \futurewk W & \Leftrightarrow \xi(W') \futurewk \xi(W)
  \end{align*}
\end{theorem}
We use the $\Regions$ from Theorem~\ref{thm:world-existence} to define
the worlds:
\begin{align*}
  \Worlds & = \RegionNames \finparfun \Regions\\
 \RegionNames & = \nats
\end{align*}
